Parallelization of Fast $\ell_1$-Minimization for Face Recognition

### 2011-03-01 paper/main.tex
adding a simulation plot which plots matrix size vs speed for tol,tol_int = 1e-1, 1e-5.  Figure doesn't import...
Working on GPU implementation section

%2MB = 2**21 bytes
%64*64*4 = 2**14 bytes = 16384 bytes per image
%... so can fit 2**7  = 128 images.
Each core has a private 32\,KB L1 data cache and a private 256\,KB L2 cache.  
Between the 8 cores, this is a total of 2\,MB L2 cache.
For the low resolution images used in sparse representation based
face recognition (on the order of $64\times64$ pixel images), this corresponds to
128 images.

With Hyperthreading
enabled, each core can support two threads simultaneously.  For floating point
instructions, each core also has a vector unit capable of performing the same
arithmetic operation on four single precision floating point values
simultaneously.

%16MB = 2**24 bytes = 16777216 bytes
%64*64*4 = 2**14 bytes = 16384 bytes per image
%... so can fit 2**10  = 1024 images.
Each processor further has 8MB of L3 cache that is shared by all four cores.
Overall, this means the algorithm has approximately 16MB of on-chip cache
available.

it is possible
to simultaneously hold up to 1024 image vectors in on-chip cache at a time.

@@

Each SMP contains its own L1-cache, which is divided between hardware managed
and software managed ("shared") memory.  Additionally, all SMPs share a common
L2-cache.  For our system, each SMP has 64 kb of L1 cache with a total of 896
kb of L1 cache/shared memory and 768kb of L2 cache. The relatively small
amount of cache on the GPU is ballanced by a significantly higher bandwidth between the
processor chip and off-chip memory (DRAM) compared to the CPU.

@@

Based on the strength of the results for our single-kernel implementation,

>>>>

% CPU CACHE DISCUSSION
%2MB = 2**21 bytes
%64*64*4 = 2**14 bytes = 16384 bytes per image
%... so can fit 2**7  = 128 images.
Each core has a private 32\,KB L1 data cache and a private 256\,KB L2 cache.  
Between the 8 cores, this is a total of 2\,MB L2 cache.
For the low resolution images used in sparse representation based
face recognition (on the order of $64\times64$ pixel images), the L2 cache
can in principle hold up to 128 image vectors.
%16MB = 2**24 bytes = 16777216 bytes
%64*64*4 = 2**14 bytes = 16384 bytes per image
%... so can fit 2**10  = 1024 images.
Each processor further has 8MB of L3 cache that is shared by all four cores.
Overall, this means the algorithm has approximately 16MB of on-chip cache
available.  This corresponds to 1024 image vectors.

With Hyperthreading enabled, each core can support two threads simultaneously.
For floating point instructions, each core also has a vector processing unit
(SSE) capable of performing the same arithmetic operation on four single
precision floating point values simultaneously.

@@

% GPU CACHE DISCUSSION
% for L2 cache
% 768KB = 786432 bytes
% 64*64*4 = 2**14 bytes = 16384 bytes per image
% 48 images
Each SMP contains its own L1-cache, which is divided between hardware managed
and software managed ("shared") memory.  Additionally, all SMPs share a common
L2-cache.  For our system, each SMP has 64 KB of L1 cache with a total of 896
KB of L1 cache/shared memory and 768KB of L2 cache. The relatively small amount
of cache (1/23 as much as CPU L3) on the GPU is ballanced by a significantly
higher bandwidth between the processor chip and off-chip memory (DRAM) compared
to the CPU.

@@

Based on the strength of the results for our single-kernel implementation, we chose to follow
a single kernel strategy for the alignment stage.

% DREW Idea... in hindsight, maybe we should still try many kernel launches, even if it
% means individual instances can't terminate early.

% Should really verify somehow that we're maxing out GPU bandwidth
